Correlation tests

### 2025-03-19 analysis/cor_tables.qmd
Convert to pandoc

```{r lood_data}
library(tidyverse)
library(corrr)
library(stats)
library(Hmisc)
library(here)
library(gt)

@@

#' Display correlation matrix using gt package with row names
#'
#' @param corr_list A list containing the correlation data frame and title
#' @return A gt table object
#' @importFrom gt gt tab_header tab_footnote cells_body everything tab_options fmt_number
create_gt_upper_triangle <- function(corr_list) {
  footnote_text <- c("* p < 0.05", "** p < 0.01", "*** p < 0.001")

@@

  # Create the gt table
  gt_table <- gt(corr_df) %>%
    # Add title as header
    tab_header(
      title = corr_list$title
    ) %>%
    # Set the Variable column as row labels
    tab_stubhead(label = "Variable") %>%
    # Add footnotes for significance levels
    tab_footnote(
      footnote = footnote_text[1],
      locations = cells_body(
        columns = everything(),
        rows = everything()
      )
    ) %>%
    tab_footnote(
      footnote = footnote_text[2],
      locations = cells_body(
        columns = everything(),
        rows = everything()
      )
    ) %>%
    tab_footnote(
      footnote = footnote_text[3],
      locations = cells_body(
        columns = everything(),
        rows = everything()
      )
    ) %>%
    # Add styling
    tab_options(
      heading.title.font.size = px(16),
      heading.subtitle.font.size = px(13),
      table.font.size = px(12),
      column_labels.font.weight = "bold",
      table.width = pct(100),
      column_labels.background.color = "#f8f8f8",
      row_group.background.color = "#f8f8f8"
    ) %>%
    # Format any numeric columns
    fmt_number(
      columns = where(is.numeric),
      decimals = 2
    )

  return(gt_table)
}
```

@@

```{r}
cor_articles <- create_correlation_table(my_df_ind, vars = c("hoad_articles", "scp_first_author_articles", "wos_first_author_articles", 
            "scp_corresponding_author_articles", "wos_corresponding_author_articles"), "Article volume")
create_gt_upper_triangle(cor_articles)
```

>>>>

```{r lood_data}
library(tidyverse)
library(corrr)
library(stats)
library(Hmisc)
library(here)

@@

#' Display correlation matrix using Pandoc table with row names
#'
#' @param corr_list A list containing the correlation data frame and title
#' @return A character string containing the Pandoc table
create_pandoc_table <- function(corr_list) {
  footnote_text <- c("* p < 0.05", "** p < 0.01", "*** p < 0.001")

@@

  # Add title
  table_title <- paste("#", corr_list$title, "\n\n")

  # Create the Pandoc table
  pandoc_table <- paste(capture.output(knitr::kable(corr_df, format = "pandoc")), collapse = "\n")

  # Add footnotes
  footnotes <- paste(footnote_text, collapse = "\n")

  return(paste(table_title, pandoc_table, "\n\n", footnotes, sep = "\n"))
}

```

@@

```{r}
#| results: asis

cor_articles <- create_correlation_table(my_df_ind, vars = c("hoad_articles", "scp_first_author_articles", "wos_first_author_articles", 
            "scp_corresponding_author_articles", "wos_corresponding_author_articles"), "Article volume")
cat(create_pandoc_table(cor_articles))
```
